Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-07-05 WSSSPE2_report/WSSSPE2_review.tex
undoing more changes

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\subsection{Papers}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
The papers that were discussed in the Citation \& Incentives group are:
\begin{itemize}
\item James Howison. Retract bit-rotten publications: Aligning incentives for
sustaining scientific software~\cite{wssspe2_howison}

\item Daniel S. Katz and Arfon M. Smith. Implementing transitive credit with
{JSON-LD}~\cite{wssspe2_katz}

\item Ian Kelley. Publish or perish: the credit deficit to making software and
generating data~\cite{wssspe2_kelley}
\end{itemize}

@@

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\subsection{Papers}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
The papers that were discussed in the Reproducibility \& Reuse \& Sharing group are:
\begin{itemize}
\item Jakob Blomer, Dario Berzano, Predrag Buncic, Ioannis Charalampidis,
Gerardo Ganis, George Lestaris and Ren\'{e} Meusel. The need for a versioned
data analysis software environment~\cite{wssspe2_blomer}

\item Ryan Chamberlain and Jennifer Schommer. Using {Docker} to support
reproducible research~\cite{wssspe2_chamberlain}

\item Neil Chue Hong. Minimal information for reusable scientific
software~\cite{wssspe2_chue_hong}

\item Tom Crick, Benjamin A. Hall, and Samin Ishtiaq. ``Can I implement your
algorithm?'': A model for reproducible research software~\cite{wssspe2_crick}

\item Bryan Marker, Don Batory, Field G. Van Zee, and Robert van de Geijn. Making
scientific computing libraries forward compatible~\cite{wssspe2_marker}

\item Stephen Piccolo. Building portable analytical environments to improve
sustainability of computational-analysis pipelines in the
sciences~\cite{wssspe2_piccolo}
\end{itemize}

@@

The papers that were discussed in the Code Testing \& Code Review group are:
\begin{itemize}
\item Thomas Clune, Michael Rilee, and Damian Rouson. Testing as an essential
process for developing and maintaining scientific software~\cite{wssspe2_clune}

\item Marian Petre and Greg Wilson. Code review for and by
scientists~\cite{wssspe2_petre}

\item Andrew E. Slaughter, Derek R. Gaston, John Peterson, Cody J. Permann,
David Andrs, and Jason M. Miller. Continuous integration for concurrent {MOOSE}
framework and application development on {GitHub}~\cite{wssspe2_slaughter}
\end{itemize}

>>>>

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\subsection{Papers}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
The papers that were discussed in the Citation \& Incentives group are:
\begin{itemize}
\item James Howison. Retract Bit-rotten Publications: Aligning Incentives for
Sustaining Scientific Software~\cite{wssspe2_howison}

\item Daniel S. Katz and Arfon M. Smith. Implementing Transitive Credit with
{JSON-LD}~\cite{wssspe2_katz}

\item Ian Kelley. Publish or Perish: The Credit Deficit to Making Software and
Generating Data~\cite{wssspe2_kelley}
\end{itemize}

@@

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\subsection{Papers}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
The papers that were discussed in the Reproducibility \& Reuse \& Sharing group are:
\begin{itemize}
\item Jakob Blomer, Dario Berzano, Predrag Buncic, Ioannis Charalampidis,
Gerardo Ganis, George Lestaris and Ren\'{e} Meusel. The Need for a Versioned
Data Analysis Software Environment~\cite{wssspe2_blomer}

\item Ryan Chamberlain and Jennifer Schommer. Using {Docker} to Support
Reproducible Research~\cite{wssspe2_chamberlain}

\item Neil Chue Hong. Minimal Information for Reusable Scientific
Software~\cite{wssspe2_chue_hong}

\item Tom Crick, Benjamin A. Hall, and Samin Ishtiaq. ``Can I Implement your
Algorithm?'': A Model for Reproducible Research Software~\cite{wssspe2_crick}

\item Bryan Marker, Don Batory, Field G. Van Zee, and Robert van de Geijn. Making
Scientific Computing Libraries Forward Compatible~\cite{wssspe2_marker}

\item Stephen Piccolo. Building Portable Analytical Environments to Improve
Sustainability of Computational-Analysis Pipelines in the
Sciences~\cite{wssspe2_piccolo}
\end{itemize}

@@

The papers that were discussed in the Code Testing \& Code Review group are:
\begin{itemize}
\item Thomas Clune, Michael Rilee, and Damian Rouson. Testing as an Essential
Process for Developing and Maintaining Scientific Software~\cite{wssspe2_clune}

\item Marian Petre and Greg Wilson. Code Review for and by
Scientists~\cite{wssspe2_petre}

\item Andrew E. Slaughter, Derek R. Gaston, John Peterson, Cody J. Permann,
David Andrs, and Jason M. Miller. Continuous Integration for Concurrent {MOOSE}
Framework and Application Development on {GitHub}~\cite{wssspe2_slaughter}
\end{itemize}
